---
title: "linear models"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


```{r}
set.seed(1)

n_samp = 250

sim_df_const = 
  tibble(
    x = rnorm(n_samp, 1, 1),
    error = rnorm(n_samp, 0, 1),
    y = 2 + 3 * x + error
  )

sim_df_nonconst = 
  sim_df_const %>% 
  mutate(
  error = error * .75 * x,
  y = 2 + 3 * x + error
)
```

show the two datasets we created

```{r}
sim_df = 
  bind_rows(const = sim_df_const, nonconst = sim_df_nonconst, .id = "data_source") 

sim_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm") +
  facet_grid(~data_source)
```

`bind_rows()`??

Fit two models

```{r}
sim_df_const %>% 
  lm(y ~ x, data = .) %>% 
  broom::tidy()

sim_df_nonconst %>% 
  lm(y ~ x, data = .) %>% 
  broom::tidy()
```


## Example of bootstrap

write a function to draw a bootstrap sample based on a dataframe

```{r}
boot_sample = function(df) {
  sample_frac(df, size = 1, replace = TRUE)
}
```

```{r}
boot_sample(sim_df_nonconst) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5)
```

Drawing many bootstrap samples

```{r}
boot_straps = 
  tibble(
    strap_number = 1:1000,
    strap_sample = rerun(1000, boot_sample(sim_df_nonconst))
  )
```

Double check everything goes right!

```{r}
bootstrap_results = 
  boot_straps %>% 
  mutate(
    models = map(strap_sample, ~lm(y ~ x, data = .x)), 
    results = map(models, broom::tidy)
  ) %>% 
  select(-strap_sample, -models) %>% 
  unnest(results)
```

Summarize these results

```{r}
bootstrap_results %>% 
  group_by(term) %>% 
  summarize(se = sd(estimate))
```


## Try the modelr package

```{r}
boot_straps = 
  sim_df_nonconst %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(y ~ x, data = .x)), 
    results = map(models, broom::tidy)
  ) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  group_by(term) %>% 
  summarize(boo_se = sd(estimate))
```

Almost the same way as we use before. 


## what if your assumptions aren't wrong

```{r}
sim_df_const %>% 
lm(y~x, data = .) %>% 
  broom::tidy()

sim_df_const %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(y ~ x, data = .x)), 
    results = map(models, broom::tidy)
  ) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  group_by(term) %>% 
  summarize(boo_se = sd(estimate))
```

**If the assumption is not violated, the results should be the same!!!**

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    boro = neighbourhood_group,
    neighborhood = neighbourhood
  ) %>% 
  filter(boro != "Staten Island") %>% 
  select(price, stars, boro, neighborhood, room_type)
```

make a quick plot

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price, color = room_type)) + 
  geom_point()
```

```{r}
airbnb_results = 
  nyc_airbnb %>% 
  filter(boro == "Manhattan") %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(price ~ stars, data = .x)), 
    results = map(models, broom::tidy)
  ) %>% 
  select(results) %>% 
  unnest(results)
```

Make a plot of the stars distribution

```{r}
airbnb_results %>% 
  filter(term == "stars") %>% 
  ggplot(aes(x = estimate)) +
  geom_density()
```

**The distribution is skewed.**




